pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-25 article.tex
Even the text is back :-)

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interpretation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\richel{
  I think we can put the interpretation in a table as well.
  Question is: do you agree with the interpretations I gave?
  Please correct me.
}

\begin{table}
  \begin{tabular}{ | r | c | c | c | }
    \hline
    \textbf{Compare with} & \textbf{E2} & \textbf{E3} & \textbf{E4} \\ 
    \hline
    \textbf{E1} & Y & Y & N \\
    \textbf{E2} & . & N & Y \\
    \textbf{E3} & . & . & Y \\
    \textbf{E4} & . & . & . \\
    \hline
  \end{tabular}
  \caption{
    Error distributions that are relevant to compare.
    E1: true tree, generative model.
    E2: true tree, best candidate model.
    E3: true tree, generative model.
    E4: true tree, best candidate model.
  }
  \label{tab:relevant_comparisions}
\end{table}

\begin{table}
  \begin{tabular}{ | r | c | p{9cm} | }
    \hline
    \textbf{Condition} & \textbf{Expectation} & \textbf{Interpretation} \\ 
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 > E2$}       & Unexpected & Novel tree prior is more related to 
      best candate than hand-picked tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 \approx E2$} & Possible   & Hand-picked tree prior is just as 
      suitable as the best candidate tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 < E2$}       & Expected   & Hand-picked tree prior is the most 
      related tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 > E3$}       & Unknown    & Novel tree prior important \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 \approx E3$} & Unknown    & Novel tree prior unimportant \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 < E3$}       & Unexpected & Twinning procedure increases 
      inference errors when using hand-picked tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 > E4$}       & Expected   & Impact of novel tree prior cannot 
      be compensated for by model selection: twin tree with low likelihood? \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 \approx E4$} & Possible   & Best candidate tree priors perform 
      equally well in true and twin tree: true and twin tree similar? \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 < E4$}       & Unexpected & Twinning procedure increases 
      inference errors  when using best tree prior candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 > E4$}       & Unexpected & Hand-picked tree prior (that equals 
      the twinning tree prior!) worse than best candidate tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 \approx E4$} & Possible   & Twin tree fits equally well to the 
      hand-picked and best candidate tree prior  \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 < E4$}       & Expected   & Hand-pick tree prior (that equals 
      the twinning tree prior) performs as expected \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
  \end{tabular}
  \caption{
    Interpretation of the different error distributions.
    This assumes that the operators ($<$, $\approx$ and $>$) to compare
    distributions are defined.
    E1: true tree, generative model.
    E2: true tree, best candidate model.
    E3: true tree, generative model.
    E4: true tree, best candidate model.
  }
  \label{tab:interpretation}
\end{table}
